Paper Wireframe

### 2018-07-27 paper_wireframe_knit.Rmd
Changes to env data munipulation

env<-read.csv('C:/cuckoo_tracking/data/spring_rainfall_NDVI_GRIMMS_TAMSAT_by_stopover_detailcoords_2018_dead.csv', h=T)

@@

@@

# rearrange

dat2<- dat2 %>% select(year, ptt, SO_startDOY, SO_endDOY, country, everything())

dat2.1<-subset(dat2, cuck_pres=='Y')

dat2.2<-dat2.1 %>% group_by(year, ptt, SO_startDOY) %>%
  summarise(cumrf=mean(cumrf, na.rm=T),
            NDVI= mean(NDVI, na.rm=T), aquaNDVI=mean(aquaNDVI, na.rm=T),
            aquaANOM=mean(aquaANOM, na.rm=T),terrNDVI=mean(terrNDVI, na.rm=T),terrANOM=mean(terrANOM, na.rm=T),tamRAIN=mean(tamRAIN, na.rm=T),tamRAINanom=mean(tamRAINanom, na.rm=T), SOlen=first(SO_endDOY)-first(SO_startDOY))

@@

@@

dat2.3<-dat2.2 %>% group_by(year, ptt) %>%
  summarise(cumrf=last(cumrf),
            NDVI= last(NDVI), 
            aquaNDVI=last(aquaNDVI),
            aquaANOM=last(aquaANOM),
            terrNDVI=last(terrNDVI),
            terrANOM=last(terrANOM),
             tamRAIN=last(tamRAIN),
            tamRAINanom=last(tamRAINanom),
            last_SOstart=last(SO_startDOY))

>>>>

env<-read.csv('C:/cuckoo_tracking/data/spring_rainfall_NDVI_GRIMMS_TAMSAT_emodis_by_stopover_detailcoords_2018_dead.csv', h=T)

names(env)[names(env)=='value']<-'precip'
names(env)[names(env)=='value2']<-'ndvi'
env$cuck_pres<-as.numeric(env$cuck_pres) # abs=1, pres=2

@@

dat2<- env[,c(2,3,4,10:22)] %>% group_by(year, ptt, SO_startDOY, variable) %>%
  summarise_all(mean,na.rm=T)

@@

# for tamsat cumrf
dat2<-dplyr::arrange(dat2, ptt, year, SO_startDOY, variable)
dat2$tamRAIN[which(!(1:21375 %in% seq(5,21375, 5)))]<-0
dat2<-dat2 %>% group_by(year, ptt, SO_startDOY) %>% dplyr::mutate(tamcumrf=cumsum(tamRAIN))

# select cond during SO..and befoe??
dat2.1<-subset(dat2, cuck_pres==2)

dat2.2<-dat2.1 %>% group_by(year, ptt, SO_startDOY) %>%
  summarise_all(mean, na.rm=T)

@@

#setwd('C:/cuckoo_tracking/data/spatial');st_write(dat_ls,'spring_linesWA.shp')

@@

dat2.3<-dat2.2 %>% group_by(year, ptt) %>%
  summarise_all(last)
